TacticToe: Learning the Game of Tactics

### 2018-01-29 tactictoe_jv.tex
minor

\section{Proof Search}\label{sec:proofsearch}

Despite the best efforts of the prediction algorithms, a selected tactic may 
not solve the current goal, proceed in the wrong direction
or even loop. For that reason, the prediction needs to be accompanied by a  
proof search mechanism that allows for backtracking and 
can choose which proof tree to extend next and in which direction.
Our search algorithm is a Monte Carlo tree search (MCTS) algorithm that relies 
on a prior evaluation function and a prior policy function. Those priors are 
learned through direct supervised learning for the policy and via the data 
accumulated during orthogonalization for the evaluation. Therefore, this MCTS 
algorithm does not need to rely on roll outs for evaluation. The 
policy and evaluation are estimated by the simple supervised k-NN algorithm 
here instead of neural networks trained through reinforcement learning in 
AlphaGo Zero~\cite{silver2017mastering}.

@@

\section{Proof Presentation}\label{sec:proofdisplay}\todo{MN + RK: add 
motivations and transitions}

@@

\todoi{Example prettified proof}

@@

\section{Comparison with Human Proofs}\todo{
  TG + RK: find describe examples.
  RK: After implementation and small experiment is done (in about 1 week) 
      Test tactictoe find new examples on new goals and manual exploration mode.
      Give feedback.
}

@@

\todo{is copied and modified}
We proposed a new proof assistant automation technique which combines 
tactic-based proof search with machine learning tactic prediction
Its implementation,
\tactictoe, achieves an overall performance of 59\% theorems on 7088 theorems  
of the \holfour standard library surpassing \eprover with 
auto-schedule. Its 
effectiveness is especially visible on 
theories which use inductive data structures, specialized decision procedures, 
and custom built simplification sets.
Thanks to the learning abilities of \tactictoe, the generated proof scripts 
usually reveal the high-level structure of the proof. %For these reasons, 
We therefore believe that predicting ITP tactics based on the current goal 
features is a very reasonable approach to automatically guiding proof search, 
and that accurate predictions can be obtained by learning from the knowledge 
available in today's large formal proof corpora. 
%And it seems to get us 
%closer to the way how humans learn to do theorem proving.

>>>>

\section{Proof Search}\label{sec:proofsearch}
Despite the best efforts of the prediction algorithms, a selected tactic may 
not solve the current goal, proceed in the wrong direction
or even loop. For that reason, the prediction needs to be accompanied by a  
proof search mechanism that allows for backtracking and 
can choose which proof tree to extend next and in which direction.
Our search algorithm is a Monte Carlo tree search (MCTS) algorithm that relies 
on a prior evaluation function and a prior policy function. Those priors are 
learned through direct supervised learning for the policy and via the data 
accumulated during orthogonalization for the evaluation. Therefore, this MCTS 
algorithm does not need to rely on roll outs for evaluation. The 
policy and evaluation are estimated by the simple supervised k-NN algorithm 
here instead of neural networks trained through reinforcement learning in 
AlphaGo Zero~\cite{silver2017mastering}.

@@

\section{Proof Presentation}\label{sec:proofdisplay}

@@

\todoi{Add an example}

@@

\section{Comparison with Human Proofs}
\todoi{Test tactictoe find new examples on new goals and manual exploration 
mode.}

@@

\todoi{Is copied and modified}
We proposed a new proof assistant automation technique which combines 
tactic-based proof search with machine learning tactic prediction
Its implementation,
\tactictoe, achieves an overall performance of 59\% theorems on 7088 theorems  
of the \holfour standard library surpassing \eprover with 
auto-schedule. Its 
effectiveness is especially visible on 
theories which use inductive data structures, specialized decision procedures, 
and custom built simplification sets.
Thanks to the learning abilities of \tactictoe, the generated proof scripts 
usually reveal the high-level structure of the proof. %For these reasons, 
We therefore believe that predicting ITP tactics based on the current goal 
features is a very reasonable approach to automatically guiding proof search, 
and that accurate predictions can be obtained by learning from the knowledge 
available in today's large formal proof corpora. 
%And it seems to get us 
%closer to the way how humans learn to do theorem proving.
